---
title: "tests_campaign"
author: "Andi Ahlers"
date: '2022-06-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages}
rm(list = ls())
library(data.table)
library(ggplot2)
library(glue)

source("ivregress.R")
```


```{r read in data}
df1 <- fread("../twitterads/data_ukraine/users_treatment.csv")
df1 <- df1[,c("id_str", "group", "condition")]

#read in individual covariate data
feats <- fread("campaign_data/features_ad_groups.csv")
feats <- feats[,c("id_str", "classifier_score", "days_since_create",
                  "friend_follow_ratio", "statuses_count")]

#read in activity data and keep only subcampaign 4
activity <- fread("campaign_data/user_activity.csv")
activity <- activity[,c("id_str", "subcamp04_tweets")]

#read in average reach for each ad group (avg over the first 25 days of campaigns)
df2 <- fread("../twitterads/data_ukraine/temp_reach_avgs.csv")


```

```{r merge covs together}
feats <- merge(feats, activity, by = "id_str")

full_df <- merge(df1, df2, by = "group")
full_df <- merge(feats, full_df, by = "id_str")

```

```{r get average classifier score for each group}
group_cov <- full_df[, .(classifier_score = mean(classifier_score), days_since_create = mean(days_since_create),
                         friend_follow_ratio = mean(friend_follow_ratio), statuses_count = mean(statuses_count),
                         subcamp04_tweets = mean(subcamp04_tweets)), by = c("group", "condition")]

```


```{r simulate outcome}
set.seed(1)
full_df[condition == "t", `:=`(outcome = rnorm(.N, .1, 1), assign = 1.0)] 
                               #cov = rnorm(.N, 0, .01))]
full_df[condition == "c", `:=`(outcome = rnorm(.N, 0, 1), assign = 0.0, avg_reach = 0)]

#full_df[condition == "c", avg_reach := 0]

```

```{r add control group to ad group level outcome}
set.seed(1)
df2[, `:=`(condition = "t", assign = 1.0)]

c_df <- copy(df2)
set.seed(1)
c_df[, `:=`(condition = "c", avg_reach = 0, assign = 0.0)]

group_df <- rbind(df2, c_df)
group_df <- merge(group_df, group_cov, by = c("group", "condition"))

```

Z: Treatment Assignment
D: Treatment Received (Compliance/Non-Compliance)
Y: Outcome 

Z serves as the instrument

```{r set dfs}
df_temp <- copy(full_df)
df_temp[,avg_reach:=NA]

S1 <- df_temp
S2 <- group_df

S_1 <- full_df
S_2 <- full_df

```

where:
* S1 is the dataframe with sample 1 - this may not have the endogenous variable
* S2 is the dataframe with sample 2 - this may not have the dependent variable
* y_var is the name of dependent variable
* regs is the list of regressors or independent variables
* ev is endogenous variable provided as a list with 1 element
* inst is the list of exogenous instruments

```{r ts 2sls}

#%% t2sls - single instrument
y_var <- "outcome"
regs <- c("classifier_score", "avg_reach", "days_since_create", "friend_follow_ratio", "statuses_count", "subcamp04_tweets") 
ev <- "avg_reach"
inst <- "assign"

#Two Sample Two Stage with Group Level as Sample 2
result <- ts2sls(S1, S2, y_var, regs, ev, inst)
print(result[1])
x_preds <- data.frame(result[2])

#Two Sample Two Stage with All Individual Level (Same Sample)
result_ind <- ts2sls(S_1, S_2, y_var, regs, ev, inst)
print(result_ind[1])
x2_preds <- data.frame(result_ind[2])

#try_lm <- lm(outcome ~ avg_reach, data = full_df)
#summary(try_lm)

#regular 2SLS where users in same ad group are assigned same reach value
res_1sample <- ivregress_2sls(full_df, y_var, regs, ev, inst, verbose = FALSE)
print(res_1sample)

.07/.015
.676/.144
.51/.126

print(result[1])
print(res_1sample)

```

```{r take xhat and run regular 2SLS with it}

xhat_full_df <- copy(full_df)
xhat_full_df <- xhat_full_df[,-"avg_reach"]
setDT(xhat_full_df)
xhat_full_df[,avg_reach := x_preds$avg_reach]

#regular 2SLS where users in same ad group are assigned same reach value
xhat_2sls <- ivregress_2sls(xhat_full_df, y_var, regs, ev, inst, verbose = FALSE)
print(xhat_2sls)


x_preds %>% select("avg_reach", "id_str")


```


```{r look at predicted reach}
results_df <- copy(full_df)
results_df$TSgrp_preds <- x_preds$avg_reach
results_df$TSind_preds <- x2_preds$avg_reach

#aggregate predicted results at the group level to compare with observed reach 

group_results <- results_df[, .(avg_grp_pred = mean(TSgrp_preds), avg_ind_pred = mean(TSind_preds), avg_class_score = mean(classifier_score)), by = c("group", "condition")]
group_results <- merge(group_results, group_df, by = c("group", "condition"))

```

```{r compare predicted reach with observed}

ggplot(group_results, aes(x = avg_reach, y = avg_grp_pred)) + geom_point() + ggtitle("Observed vs Average Predicted for Group TS2SLS") + xlab("Observed Group Reach") + 
    ylab ("Average of TS2SLS Predictions")

ggplot(group_results, aes(x = avg_reach, y = avg_ind_pred)) + geom_point() + ggtitle("Observed vs Average Predicted for Individual TS2SLS") + xlab("Observed Group Reach") + 
    ylab ("Average of TS2SLS Predictions")

```


```{r preds by ad group}

ggplot(results_df[condition == "t"], aes(x = group, y = TSgrp_preds)) + geom_point() + 
    ggtitle("Predicted Indidivual Reach by Ad Group (Treatment)") + xlab("Group") + 
    ylab ("Individual TS2SLS Predictions") + 
    geom_point(data = group_results[condition == "t"], aes(x = group, y = avg_reach), color = "brown2")

 ggplot(results_df[condition == "c"], aes(x = group, y = TSgrp_preds)) + geom_point() + 
    ggtitle("Predicted Indidivual Reach by Ad Group (Control)") + xlab("Group") + 
    ylab ("Individual TS2SLS Predictions") + 
    geom_point(data = group_results[condition == "t"], aes(x = group, y = avg_reach), 
               color = "darkturquoise")


```


```{r look at distributions of the predicted reach within each ad group}

treat_plots <- c()
for (i in 1:27){
    ad_grp <- i - 1
    temp_df <- results_df[group == i & condition == "t"]
    
    p <- ggplot(temp_df, aes(x = TSgrp_preds)) +
        geom_histogram(binwidth = .0075) + labs(title = glue("Ad Group {ad_grp} Treatment"))
    treat_plots[[i]] <- p
}

cont_plots <- c()
for (i in 1:27){
    ad_grp <- i - 1
    temp_df <- results_df[group == i & condition == "c"]
    
    p <- ggplot(temp_df, aes(x = TSgrp_preds)) +
        geom_histogram(binwidth = .0075) + labs(title = glue("Ad Group {ad_grp} Control"))
    cont_plots[[i]] <- p
}


treat_plots
cont_plots

```


```{r auto data, eval = FALSE}
# iveregress - single instrument

S <- df2
y_var  <- "price"
regs <- c("weight", "mpg")
ev <- "mpg"
inst <- "headroom"
result <- ivregress_2sls(S, y_var, regs, ev, inst, verbose = T)
result

```



```{r check auto data, eval = FALSE}

df1 <- fread("auto_data.csv")
df1[, weight2 := weight * weight]
df2 <- copy(df1)
df1$mpg <- NA

S1 <- df1
S2 <- df2

#%% iveregress - single instrument

S <- df2
y_var  <- "price"
regs <- c("weight", "mpg")
ev <- "mpg"
inst <- "headroom"
result <- ivregress_2sls(S, y_var, regs, ev, inst, verbose = T)
result

#%% t2sls - single instrument

y_var <- "price"
regs <- c("weight", "mpg")
ev <- "mpg"
inst <- "headroom"
result <- ts2sls(S1, S2, y_var, regs, ev, inst)
print(result)

```

## Two Stage Bootstrap

**Two stage**

```{r}
library(MASS)  
library(fixest)
library(data.table)

df1 <- fread("campaign_data/users_treatment.csv")
df1[, id_str := as.character(id_str)]
df1 <- df1[, .(id_str, group, condition, block)]
n_groups <- length(unique(df1$group))
n_users <- n_distinct(df1$id_str)
n_blocks <- n_distinct(df1$block)
df1[, .N, block][, min(N)]  # check min no. of users per block

set.seed(02139)
Z <- rep(c(0, 1), n_groups)  # instrument (treatment assignment)
D <- rbeta(n_groups * 2, 2,5) * 0.4  # reach
D[Z == 0] <- 0
Y <- floor(rbeta(n_users, 1, 50) * 100)  # count outcome 
df1$Y <- Y
df1

df1

#  ad gruop data
df2 <- data.frame(Z, D, 
                  group = rep(seq(1, n_groups), each = 2), 
                  condition = rep(c("c", "t"), n_groups), 
                  group_name = seq(1, n_groups * 2))


# currently no fixed effect involved
glm_2stage <- function(df1, df2){
  stage1 <- glm(D~Z, df2, family = "gaussian")  # these two lines assume 2-sample setup (do we want to do/assume this?)
  stage1_predicted <- predict.lm(stage1, df2)
  
  # estimate D_hat
  df <- left_join(df1, df2, by = c("group", "condition"))
  df$D_hat <- sapply(df$group_name, function(x) stage1_predicted[x])
  # set D_hat to 0 for control group (?)
  df$D_hat <- ifelse(df$condition == "c", 0, df$D_hat)
  
  # calculate residuals for residuals inclusion
  df$residuals <- sapply(df$group_name, function(x) stage1$residuals[x])
  
  stage2 <- glm(Y ~ D_hat + residuals, df, family = "quasipoisson")
  return(summary(stage2)$coefficients)
}

# try to include fixed effects 
df <- data.table(left_join(df1, df2))
df[, x1 := rnorm(.N)]
glm_2sls <- function(df, only.coef = FALSE) {
    # https://github.com/lrberge/fixest/issues/176
    # stage1
    stage1 <- feols(Y ~ x1 | block | D ~ Z, data = df)  
    df$stage1_resids <- resid(summary(stage1, stage = 1))  # get residuals for residual inclusion/control function approach in stage2
    
    # stage2
    stage2 <- feglm(Y ~ x1 + stage1_resids | block, data = df, family = "quasipoisson", only.coef = only.coef)
    return(stage2)
}
glm_2sls(df)
```

**Bootstrap**

```{r}
B <- 100
coefficients <- list()
pairwise <- TRUE
for (b in 1:B){
  # sample ad group level data frame
  if (pairwise){
    trt_idx <- sample(1:n_groups, n_groups, replace = T)
    df2_b <- rbind(df2[df2$condition == "t",][trt_idx, ], df2[df2$condition == "c",][trt_idx, ])
  } else{
    trt_idx <- sample(1:n_groups, n_groups, replace = T)
    ctr_idx <- sample(1:n_groups, n_groups, replace = T)
    df2_b <- rbind(df2[df2$condition == "t",][trt_idx, ], df2[df2$condition == "c",][ctr_idx, ])
  }
  
  # sample individual level data frame
  # currently no sample by block involved
  df1_b <- c()
  # re-sample within each ad group
  for (i in 1:nrow(df2_b)){
    cdt <- df2_b$condition[i]
    grp <- df2_b$group[i]
    tmp <- df1 %>% filter(condition == cdt) %>% filter(group == grp)
    idx <- sample(1:nrow(tmp), nrow(tmp), replace = T)
    df1_b <- rbind(df1_b, tmp[idx, ])
    
  }
  coefficients[[b]] <- glm_2stage(df1_b, df2_b)
  
}

```


